---
title: "AIDS Drug Test"
author: "Dominique Repp"
date: "May 4TH 2019"
output: html_document
   
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avast <- filter(avast,LBGT=="yes")

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orintation

The first question is this, does the abacavirinol have any affect on whether one contacts AIDS or not?

$h_0:$ avacavirinol has no effct on whether one contracts AIDS or not

$h_a:$ avacavirinol has an effct on whether one contracts AIDS or not


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
For each hypothis test the graphical summery will be a bar plot, the numberical summery will be a cross tublation, and a chi-squared test will be used for the inferential results. 

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->Based on the data provvided from the graph, it seems to be a a low incidents of HIV affection in the LBGT group thats taking the drug. For thoes taking the drug there seem to be a 40% less chance of contracting HIV. 

###Plot barplots

```{r}
barchartGC(~infected + treatment,data=avast,type="percent")
```



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-- 
  
###Numerical Summaries  

```{r}
table1 <- xtabs(~infected + treatment, data=avast)
rowPerc(table1)
colPerc(table1)
```
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->From our inferintral results we find that there is a low p-vale of 0, and a chi-square value of 1.


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
From our infurential results the drug is worinking for the people in the LGBT groug, while working less, or in a backword fashion for thoes taking the plocebo.